---
title: "qacr::stats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### **A quick guide to the "stats" function of the qacr package**
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo=TRUE, eval=FALSE, error=FALSE, warning=FALSE, message=FALSE}
library(qacr)
```


This function provides descriptive statistics for a quantitative variable (unquoted). If no keyword arguments for statistics are provided, default values are used. Default statistics: c("n", "mean", "sd")
```{r include=TRUE}
stats(oil,operator)
soils
```

You supply statistics argument with the "statistic" parameter. You can pass single statistic or multiple statistics as a list object.
Singe statistic:
```{r include=TRUE}
stats(oil,operator,statistics = c("median"))
```

Multiple statistics:
```{r include=TRUE}
stats(soils,pH,statistics = c("median","mean","sd"))
```


You can supply as many grouping variables as needed. 
```{r include=TRUE}
stats(soils, N, Group,Contour,Depth)
```



You can pass multiple statistics and multiple grouping variable at the same time.
```{r include=TRUE}
stats(soils, pH, Group, Contour, statistics=c("mean","median","sd"), Block, Depth)
```


User-defined functions can also be used as the 'statistic'. It's passed using the statistic parameter:
```{r include=TRUE}
#custom statistic
my_n <- function(xs) length(xs)

#calling the custom statistic
stats(soils, pH, statistic = c("my_n"))
```


User-defined functioned can also be passed alongside other statistics:
```{r include=TRUE}
stats(soils, pH, Group, Contour, statistics=c("my_n","mean"), Block, Depth)
```


Other optionalinputs into the function include the 'na.rm' parameter. When TRUE, NAs are removed. Default is TRUE
```{r include=TRUE}
stats(soils, pH, statistics=c("mean","median","sd"), Depth, na.rm=FALSE)
```


Another optional input is digit, which is the number of decimal points to print. Default = 2. 
```{r include=TRUE}
stats(soils, pH, statistics=c("mean","median","sd"), Depth, na.rm=FALSE, digits=4)
```
























