---
title: "tab_vingette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tab_vingette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qacr)

```


```{r, include=TRUE}
tab(venues, state)
```
Creates a table with the number of venues in each state and calculates the percent of toal venues in each state


```{r, include=T}
tab(venues, state, sort = T)
```
Sorts the previous table based on number of venues

```{r, include=T}
tab(venues, state, sort = T, na.rm = T, total = T)
```
Removes all missing observations from the data set and adds a total row to the table


```{r, include=T}
tab(venues, state, sort = T, total = T, digits = 4)
```
Rounds all percentages off to the fourth decimal place


```{r, include=T}
tab(venues, state, sort = T, total = T, maxcat = 15)
```
Only makes a table of the 15 states with the most venues and adds all other states up in an other category


```{r, include=T}
tab(venues, state, sort = T, total = T, minp = .1)
```
Only makes a table with states that have over a tenth of the overall venues, adds up all others in an other category



